---
title: "Final Project Part 2"
author: "Qi An and Hanwen Xing"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Two csv files used for this Rmd file are the feature matrices outputed from our Python file after image processing and feature selections. The main purpose of this Rmd file is to perform Exploratory Data Analysis on two feature matrix data sets and Data Mining on model results by using clustering. 

## First Dataset

```{r}
library(factoextra)
library(gridExtra)
```

```{r}
#Data Preparation
df <- read.csv('~/Desktop/Data Mining/Project2/first_data.csv')
df <- df[, -dim(df)[2]]
characters <- sub("_.*", "", df[,1])
avg <- matrix(NA, ncol=32, nrow=5)
for(i in 1:5){
  char <- unique(characters)[i]
  temp <- df[grepl(char, df$X), ][,-1]
  avg[i,] <- apply(temp, 2, mean)
}
rownames(avg) <- unique(characters)

#Metrics 1
par(mfrow = c(2, 3))
barplot(avg[1,], ylim = c(0,30), main = 'Distribution of wu')
barplot(avg[2,], ylim = c(0,30), main = 'Distribution of kang')
barplot(avg[3,], ylim = c(0,30), main = 'Distribution of yi')
barplot(avg[4,], ylim = c(0,30), main = 'Distribution of ji')
barplot(avg[5,], ylim = c(0,30), main = 'Distribution of fu')

#Metric2 - Euclidean Distance
dist(avg,method="euclidean")

```

## First Dataset Clustering

```{r}
#Clustering Method-kmeans
km_out <- kmeans(df[,-1], centers=5)

#Clustering Results Analysis
#result <- data.frame(characters = characters, cluster = km_out$cluster)
table(km_out$cluster)
table(km_out$cluster, characters)

index <- which(apply(df[,-1],2,sum)==0)+1
fviz_cluster(km_out, data = df[,-c(1,index)])

#Trying to decrease clustering sizes
k2 <- kmeans(df[,-1], centers=2)
k3 <- kmeans(df[,-1], centers=3)
k4 <- kmeans(df[,-1], centers=4)

p1 <- fviz_cluster(k2, geom = "point", data = df[,-c(1,index)]) + 
  ggtitle("k = 2")
p2 <- fviz_cluster(k3, geom = "point",  data = df[,-c(1,index)]) + 
  ggtitle("k = 3")
p3 <- fviz_cluster(k4, geom = "point",  data = df[,-c(1,index)]) + 
  ggtitle("k = 4")
p4 <- fviz_cluster(km_out, geom = "point",  data = df[,-c(1,index)]) + 
  ggtitle("k = 5")

grid.arrange(p1, p2, p3, p4, nrow = 2)

#Quantitatively
km_out$withinss
km_out$betweenss

avg_ts <- matrix(NA, ncol=32, nrow=5)
for (i in 1:5){
  df_new <- df[,-1]
  cluster <- df_new[km_out$cluster==i,]
  avg_ts[i,] <- apply(cluster,2,mean)
}
plot(avg_ts[1,], type = 'l', xaxt='n',
     ylab = 'Average Count',
     main = 'Average Feature Count across Clusters')
lines(avg_ts[2,], col = 'blue')
lines(avg_ts[3,], col = 'red')
lines(avg_ts[4,], col = 'green')
lines(avg_ts[5,], col = 'pink')

```


## Second Dataset

```{r}
df <- read.csv('~/Desktop/Data Mining/Project2/second_data.csv')
df <- df[, -dim(df)[2]]
characters <- sub("_.*", "", df[,1])
avg <- matrix(NA, ncol=32, nrow=5)
for(i in 1:5){
  char <- unique(characters)[i]
  temp <- df[grepl(char, df$X), ][,-1]
  avg[i,] <- apply(temp, 2, mean)
}
rownames(avg) <- unique(characters)

#Metrics 1
par(mfrow = c(2, 3))
barplot(avg[1,], ylim = c(0,30), main = 'Distribution of wu')
barplot(avg[2,], ylim = c(0,30), main = 'Distribution of cheng')
barplot(avg[3,], ylim = c(0,30), main = 'Distribution of ge')
barplot(avg[4,], ylim = c(0,30), main = 'Distribution of shang')
barplot(avg[5,], ylim = c(0,30), main = 'Distribution of wan')

#Metric2 - Euclidean Distance
dist(avg,method="euclidean")

```
## Second Dataset Clustering

```{r}
km_out <- kmeans(df[,-1], centers=5)

#Clustering Results Analysis
#result <- data.frame(characters = characters, cluster = km_out$cluster)
table(km_out$cluster)
table(km_out$cluster, characters)

index <- which(apply(df[,-1],2,sum)==0)+1
fviz_cluster(km_out, data = df[,-c(1,index)])

#Trying to decrease clustering sizes
k2 <- kmeans(df[,-1], centers=2)
k3 <- kmeans(df[,-1], centers=3)
k4 <- kmeans(df[,-1], centers=4)

p1 <- fviz_cluster(k2, geom = "point", data = df[,-c(1,index)]) + 
  ggtitle("k = 2")
p2 <- fviz_cluster(k3, geom = "point",  data = df[,-c(1,index)]) + 
  ggtitle("k = 3")
p3 <- fviz_cluster(k4, geom = "point",  data = df[,-c(1,index)]) + 
  ggtitle("k = 4")
p4 <- fviz_cluster(km_out, geom = "point",  data = df[,-c(1,index)]) + 
  ggtitle("k = 5")

grid.arrange(p1, p2, p3, p4, nrow = 2)
```

